\Large \bf \Toolname: Precise False Sharing Detection for COTS Binaries

### 2014-11-06 HotOS'15/paper.tex
Changed the described purpose of the selective heap shadowing a bit.

\paragraph{Selective Heap Sampling}
Selective heap sampling is a biased variant of uniform heap sampling that allows a user to guide the sampler to only focus
on specific types of data. This is beneficial when one is trying to solve specific performance problems related to a subset
of the data being accessed by the application.

>>>>

\paragraph{Selective Heap Sampling}
Selective heap sampling is a biased variant of uniform heap sampling that enables \Toolname{} to only focus on the subset
of the heap that is believed to contain objects that participate in false sharing. Selective heap sampling builds typesets
for only a subset of proxy memory associated with specific allocation points.

Selective heap sampling also allows a user to guide the sampler to only focus on specific types of data. This is beneficial
when one is trying to solve specific performance problems related to a subset of the data being accessed by the application.
